Black swans in ecological time series\\ Black swans in population dynamics\\ Heavy-tailed ecological time series\\ Black swans in ecological dynamics\\ Black swan ecological dynamics\\ \ldots

### 2014-11-01 text/ms.tex
Minor edits

There is compelling anecdotal evidence for ecological black swans, but
systematic evidence has been elusive. A survey of ecologists indicated that
surprising outcomes of field experiments are far more common than we assume
\citep{doak2008}, and a number of major environmental events on geologic and
contemporary time scales could be considered to have caused ecological black
swans \citep{nunez2012}.
% TODO: pull anecdote from that study
Black swans, or heavy tailed distributions, have been discovered in time-series
of marine microbe populations \citet{segura2013} and time to extinction for
experimental waterflea populations \citet{drake2014}. As far as we can tell
there have been two systematic surveys for ecological black swans, one in North
American breeding birds and the Global Population Dynamics Database, that found
little clear evidence for them \citep{keitt1998,allen2001,halley2002}.
Nevertheless there are methodological challenges to their detection
\citep{allen2001,ward2007}.

>>>>

There is compelling anecdotal evidence for ecological black swans, but
systematic evidence has been elusive. A survey of ecologists indicated that
surprising outcomes of field experiments are far more common than we assume
\citep{doak2008}, and a number of major environmental events on geologic and
contemporary time scales could be considered to have caused ecological black
swans \citep{nunez2012}.
% TODO: pull anecdote from that study
Black swans, or heavy tailed distributions, have been discovered in time-series
of marine microbe populations \citet{segura2013} and time to extinction for
experimental waterflea populations \citet{drake2014}. As far as we can tell
there have been two systematic surveys for ecological black swans: one with North
American breeding birds and the other with the Global Population Dynamics Database, which 
 found little clear evidence for them \citep{keitt1998,allen2001,halley2002}.
Nevertheless there are methodological challenges to their detection
\citep{allen2001,ward2007}.

### 2014-11-01 text/supp.tex
Minor edits

\begin{centering}
\LARGE
Supporting Material\\[1.0em]
\end{centering}

@@

We also fitted a Ricker-logistic model:
\begin{align*}
x_t &= x_{t-1} + r_{\mathrm{max}}\left(1 - \frac{N_{t-1}}{K}\right) + \epsilon_t\\
\epsilon_t &\sim \mathrm{Student\mhyphen t}(\nu, 0, \sigma),
\end{align*}
where $r_\mathrm{max}$ represents the theoretical maximum population growth
rate that is obtained when $N$ (abundance) $= 0$. The parameter $K$ represents
the carrying capacity and, as before, $x_t$ represents the $\log$ transformed
abundance at time $t$. The Ricker-logistic model assumes a linear decrease in
population growth rate ($x_t - x_{t-1}$) with increases in abundance ($N_t$).
In contrast, the Gompertz model assumes a linear decrease in population growth
rate with increases in \textit{log} abundance ($x_t$) (REF).

@@

\noindent
The GPDD IDs used in our analysis. See \url{https://github.com/seananderson/heavy-tails}.

>>>>

\begin{centering}
\LARGE
Supporting Information\\[1.0em]
\end{centering}

@@

We also fitted a Ricker-logistic model:
\begin{align*}
x_t &= x_{t-1} + r_{\mathrm{max}}\left(1 - \frac{N_{t-1}}{K}\right) + \epsilon_t\\
\epsilon_t &\sim \mathrm{Student\mhyphen t}(\nu, 0, \sigma),
\end{align*}
where $r_\mathrm{max}$ represents the theoretical maximum population growth
rate that is obtained when $N_t$ (abundance at time $t$) $= 0$. The parameter $K$ represents
the carrying capacity and, as before, $x_t$ represents the $\log$ transformed
abundance at time $t$. The Ricker-logistic model assumes a linear decrease in
population growth rate with increases in abundance.
In contrast, the Gompertz model assumes a linear decrease in population growth
rate with increases in \textit{log} abundance ($x_t$) \citep[e.g.][]{thibaut2012}.

@@

\noindent
The GPDD IDs used in our analysis.
